---
title: "Collaboration and Clean up"
author: "Ravi"
date: "12/24/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment #7-collaboration on repository and data cleanup
 
 
 ## Populate the missing values in the Area variable with an appropriate values (Birmingham, Coventry, Dudley, Sandwell, Solihull, Walsall or Wolverhampton)

```{r fill missing data, echo=FALSE}
 library(tidyr)
dirty_data <- read.csv("~/Documents/ANLY 510/dirty_data.csv")
 
 dirty_frame<- dirty_data
dirty_frame
 data_filled<-fill(dirty_frame, Area, .direction = c("down"))
data_filled
```
 ##Remove special characters, padding (the white space before and after the text) from Street 1 and Street 2 variables. Make sure the first letters of street names are capitalized and the street denominations are following the same standard (for example, all streets are indicated as “str.”, avenues as “ave.”, etc.
```{r Removes Special Characters, include=FALSE}

 data_filled$Street = gsub("[^A-Za-z ]", " ",data_filled$Street)
 data_filled$Street = gsub("(?<=[\\s])\\s*|^\\s+|\\s+$", "", data_filled$Street, perl=TRUE)
 data_filled$Street
 data_filled$Street.2 = gsub("[^A-Za-z ]", " ", data_filled$Street.2)
 data_filled$Street.2 = gsub("(?<=[\\s])\\s*|^\\s+|\\s+$", "", data_filled$Street.2, perl=TRUE)
 data_filled$Street.2
 
 data_filled$Street = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", data_filled$Street, perl=TRUE)
 data_filled$Street.2 =  gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", data_filled$Street.2, perl=TRUE)
 
 # This Code will Make sure the first letters of street names are capitalized and the street denominations are following the same standard 
 #(for example, all streets are indicated as âstr.â, avenues 
 install.packages('gsubfn')
 library('gsubfn')
 
 patterns     <- c("Lane", "Road", "Avenue", "Green", "Hospital", "Village", "Center", "Drive", "Circle", "Park","Street")
 replacements <- c("Lan.",  "Rd.", "Ave.", "Gr.","Hosp.","Vil.","Ctr.", "Dr.", "Cr.","Pk.","Str.")

data_filled$Street = gsubfn("\\b\\w+\\b", as.list(setNames(replacements, patterns)), data_filled$Street)
data_filled$Street.2 =  gsubfn("\\b\\w+\\b", as.list(setNames(replacements, patterns)), data_filled$Street.2)
```
 
 #If the value in Street 2 duplicates the value in Street 1, remove the value in Street 2
 
```{r remove duplicates, echo=TRUE}

i = 1

 while(i < nrow(data_filled )) 
 {
  if(data_filled$Street[i] == data_filled$Street.2 [i]) 
   {
     data_filled$Street.2 [i] = ""
   }
   i = i+1
 }
```
 ## Remove the “Strange HTML column”

```{r removes Strange Column, echo=TRUE}

 # This code will remove the “Strange HTML column”
data_filled = subset(data_filled[,1:4])
head(data_filled)
write.csv(data_filled,"~/Documents/ANLY 510/clean_data.csv" )
```
 